Parallelization of the Probabilistic Roadmap Method with GPU Acceleration

### 2016-07-27 paper/paper.tex
stand besprechung

This means, that for $i=0,...,n-1$ the vertices with indices $\mathrm{ dest[dsp[i]],..., dest[dsp[i]+cnt[i]-1] }$ are the ones connected to vertex $i$ by an edge.
The polytopes are given by the user as convex hull of a list of vertices. However, to determine the edge graph only from the vertices is a nontrivial task, which is done by Matlab using builtin high level functions.

@@

Code \ref{code4} exemplarily shows the class definition of the robot configuration space.
The geometry and robot data does not change during runtime
and is load\-ed once at the beginning and copied to the GPU by the 
\texttt{init}
function.
The indicator function gets as input a list of start and end points $q_{start}^j, q_{end}^j, j=0,...,N$ and checks now for each pair, if the indicator function is always 0 on the line in between.
\begin{equation}
	\mathrm{res[j]}=\begin{cases}
		%0	&\text{if $I(q)=0$ f.a. $q \in \left[q_{start}^j, q_{end}^j\right]_{\Delta q}$} \\
		0	&\text{if\ \ } \forall q \in \left[q_{start}^j, q_{end}^j\right]_{\Delta q} : I(q)=0 \\
		1	&\text{else}
	\end{cases}
\end{equation}
This computation is done by calling the kernel in Code \ref{code5}.
The start and end points are stored in structures of arrays defined by
\begin{equation}
\begin{aligned}
	q_{start}^j &= (q_s^j , q_s^{j+N_{buf}} , ... , q_s^{j+(d-1)*N_{buf}})^T\\
	q_{end}^j &= (q_e^j , q_e^{j+N_{buf}} , ... , q_e^{j+(d-1)*N_{buf}})^T
\end{aligned}
\end{equation}
As the PRM solver only needs to know, which start and end points can be connected by a line, the kernel delivers exactly this minimal necessary information. 
CPU and communication time is also saved by computing interpolating points directly on the GPU and not to exchange them.
Algorithms \ref{host} and \ref{kernel} show in pseudo code, how the work is split between host and device.

\begin{algorithm}\label{host}
	\KwData{$q_s$, $q_e$, N, $N_{buf}$}
	\KwResult{res}
	compute distances $d_j = \abs{q_{end}^j - q_{start}^j}$ \;
	$\mathrm{testnum[j]} = d_j/{\Delta q}$: number of threads for each line \;
	$\mathrm{testpos[j]} = \mathrm{thread\ displacements}$ \;
	reset res \;
	call kernel with $\sum_{j=0}^N \mathrm{testnum[j]}$ threads\;
	\caption{Host indicator function}
\end{algorithm}

\begin{algorithm}\label{kernel}
	\KwData{arrays $q_s$, $q_e$, testpos, testnum and threadindex}
	\KwResult{res}
	compute associated edge number $j$, defined by $testpos[j] \leq threadindex \le testpos[j]+testnum[j]$ \;
	$c = (\mathrm{threadindex - testpos[j]}) / (\mathrm{testnum[k]}-1) $ \;
	$q=c q_{start}^j + (1-c) q_{end}^j $ \;
	calculate robot kinematics $T_0(q), ..., T_d(q) $\;
	$\mathrm{res\_tmp} = 0; $ \;
	\For{all registered pairs pairs of polytopes $P, Q$}{
		$\mathrm{res\_tmp}=\mathrm{separating\_vector\_algorithm}(P, T_{i_P}, Q, T_{i_Q})$ \;
		\If{$\mathrm{res\_tmp} \neq 0$}{
			$\mathrm{res}[j]=\mathrm{res\_tmp}$ \;
			break \;
		}
	}
	\caption{Robot kernel: code for one thread}
\end{algorithm}

>>>>

This means, that for $i=0,...,n-1$ the vertices with indices \texttt{ dest[dsp[i]],...,dest[dsp[i]+cnt[i]-1] } are the ones connected to vertex $i$ by an edge.
The polytopes are given by the user as convex hull of a list of vertices. However, to determine the edge graph only from the vertices is a nontrivial task, which is done by Matlab using builtin high level functions.

@@

Code \ref{code4} exemplarily shows the class definition of the robot configuration space.
The geometry and robot data does not change during runtime
and is load\-ed once at the beginning and copied to the GPU by the 
\texttt{init}
function.
The indicator function gets as input a list of start and end points $q_{start}^j, q_{end}^j, j=0,...,N$ and checks now for each pair, if the indicator function is always 0 on the line in between.
\begin{equation}
	\mathrm{res[j]}=\begin{cases}
		%0	&\text{if $I(q)=0$ f.a. $q \in \left[q_{start}^j, q_{end}^j\right]_{\Delta q}$} \\
		0	&\text{if\ \ } \forall q \in \left[q_{start}^j, q_{end}^j\right]_{\Delta q} : I(q)=0 \\
		1	&\text{else}
	\end{cases}
\end{equation}
This computation is done by calling the kernel in Code \ref{code5}.
The start and end points are stored in structures of arrays defined by
\begin{equation}
\begin{aligned}
	q_{start}^j &\defgl (q_s^j , q_s^{j+N_{buf}} , ... , q_s^{j+(d-1)*N_{buf}})^T\\
	q_{end}^j &\defgl (q_e^j , q_e^{j+N_{buf}} , ... , q_e^{j+(d-1)*N_{buf}})^T
\end{aligned}
\end{equation}
As the PRM solver only needs to know, which start and end points can be connected by a line, the kernel delivers exactly this minimal necessary information. 
CPU and communication time is also saved by computing interpolating points directly on the GPU and not to exchange them.
Algorithms \ref{host} and \ref{kernel} show in pseudo code, how the work is split between host and device.

\begin{algorithm}\label{host}
	\KwData{$q_s$, $q_e$, N, $N_{buf}$}
	\KwResult{res}
	compute distances $d_j = \abs{q_{end}^j - q_{start}^j}$ \;
	$\mathrm{testnum[j]} = d_j/{\Delta q}$: number of threads for each line \;
	$\mathrm{testpos[j]} = \mathrm{thread\ displacements}$ \;
	reset res \;
	call kernel with $\sum_{j=0}^N \mathrm{testnum[j]}$ threads \;
	\caption{Host indicator function}
\end{algorithm}

\begin{algorithm}\label{kernel}
	\KwData{arrays $q_s$, $q_e$, testpos, testnum and threadindex}
	\KwResult{res}
	compute associated edge number $j$, defined by $testpos[j] \leq threadindex \le testpos[j]+testnum[j]$ \;
	$c = (\mathrm{threadindex - testpos[j]}) / (\mathrm{testnum[k]}-1) $ \;
	$q=c q_{start}^j + (1-c) q_{end}^j $ \;
	calculate robot kinematics $T_0(q), ..., T_d(q) $ \;
	$\mathrm{res\_tmp} = 0$ \;
	\For{all registered pairs pairs of polytopes $P, Q$}{
		$\mathrm{res\_tmp}=\mathrm{separating\_vector\_algorithm}(P, T_{i_P}, Q, T_{i_Q})$ \;
		\If{$\mathrm{res\_tmp} \neq 0$}{
			$\mathrm{res}[j]=\mathrm{res\_tmp}$ \;
			break \;
		}
	}
	\caption{Robot kernel: code for one thread}
\end{algorithm}
